\documentclass[12pt]{article}
\usepackage{usecases}
\begin{document}
\begin{usecase}

\addtitle{Use Case 3}{Define activities} 

%Scope: the system under design
\addfield{Scope:}{System-wide}	
%Primary Actor: Calls on the system to deliver its services.
\addfield{Primary Actor:}{Project leader and Developer}

%Stakeholders and Interests: Who cares about this use case and what do they want?
\additemizedfield{Stakeholders and Interests:}{
	\item Project Leader: Needs add activities to projects and modify them.
	\item Developer: Needs add activities to projects and modify them. Also needs to register hours worked on given activity.
	
}
\addfield{Description:}{Makes it possible to create an activity connected to a project, add developers to the activity and assign workhours to the activity}
%Main Success Scenario: A typical, unconditional happy path scenario of success.
\addscenario{Main Scenario:}{
	\item Lets the users create activities.
	\item The users can create activities, defined by name, description and allocated workhours.
	\item Lets the user connect developers to an activity.
	\item Lets the users define the expected start and end dates of the activity. It's possible to assign an endDate without startDate and vice versa.
	\item Lets the developers define the actual hours of work put into the activity. It's possible to set the final workhours and add work hours while working.
}

%Extensions: Alternate scenarios of success or failure.
\addscenario{Alternative Scenarios:}{
	\item[2.a] No name assigned:
		\begin{enumerate}
		\item[1.] The activity will be assigned a default name.
		\item[2.] The activitys name can be modified at a later time
		\end{enumerate}
	\item[2.b] Description not assigned:
		\begin{enumerate}
		\item[1.] The activity will have no description.
		\item[2.] The description of the activity can be set at a later time.
		\end{enumerate}
	\item[3.a] Adding same user twice
		\begin{enumerate}
		\item[1.] System throws an error
		\item[2.] System returns to 3.
		\end{enumerate}
	\item[4.a]  If start date not assigned:
		\begin{enumerate}
		\item[1.] If start date is not assigned the activity will have no start date.
		\item[2.] The start date can be modified later.
		\end{enumerate}
	\item[4.b] If end date not assigned:
		\begin{enumerate}
		\item[1.] If end date is not assigned, the activity will have no end date.
		\item[2.] The end date can be modified later.
		\end{enumerate}
	\item[4.c] End date is before start date
		\begin{enumerate}
		\item[1.] The system will show an error.
		\item[2.] The system will go back to 4.
		\end{enumerate}
	\item[5.a] Define negative hours of work
		\begin{enumerate}
		\item[1.] System returns an error
		\item[2.] System returns user to 5.
		\end{enumerate}
}
\end{usecase}
\end{document}